True versus apparent shapes of astrophysical bow shocks

### 2017-06-14 papers/Paper1/sec-quadrics-observations.tex
Add Herschel material to paper
And add KDE for Herschel and Orion arcs in the figures
Finish caption for Figure 25

\begin{figure*}
  \centering
  \includegraphics[width=\linewidth]{figs/mipsgal-Rc-R90-vs-Herschel}
  \caption[]{Comparison of RSG/AGB arcs with OB star arcs.}
  \label{fig:herschel-compare-mipsgal}
\end{figure*}

>>>>

\begin{figure*}
  \centering
  \setkeys{Gin}{width=0.48\linewidth}
  \includegraphics[trim=10 0 60 30, clip]{figs/alphaori-imageplot}
  \includegraphics[trim=10 0 60 30, clip]{figs/mucep-imageplot}
  \includegraphics[trim=10 0 60 30, clip]{figs/rhya-imageplot}
  \includegraphics[trim=10 0 60 30, clip]{figs/rleo-imageplot}
  \includegraphics[trim=10 0 60 30, clip]{figs/uuaur-imageplot}
  \includegraphics[trim=10 0 60 30, clip]{figs/v1943sgr-imageplot}
  \includegraphics[trim=10 0 60 30, clip]{figs/xpav-imageplot}
  \caption{RSG and AGB shells observed with Herschel.  Selected
    Class~I sources (``fermata-like'') from the MESS survey
    \citet{Cox:2012a}.  Left panels show PACS \SI{70}{\um} surface
    brightness (blue) and \SI{160}{\um} (orange).  Right panels show
    tracing of the bow shock arc (red symbols) and circle fit (magenta
    lines and symbols) superimposed on a low-contrast image of the
    \SI{70}{\um} surface brightness.}
  \label{fig:herschel-arc-fits}
\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[width=\linewidth]{figs/mipsgal-Rc-R90-vs-Herschel}
  \caption[]{Comparison of RSG/AGB arcs with OB star arcs.  }
  \label{fig:herschel-compare-mipsgal}
\end{figure*}
